### 2018-02-01 includes/stringfuzz.tex
Fixing jarring command.
fix to grammar
Removing reference to ifaz's tech report.

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}
We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project 
contains \linesInFuzzer{} lines of code, it takes an average of 
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be 
installed from source, or from the Python PIP package
repository.\footnote{The link to the source code will be added after double-blind review.}

@@

\subsubsection{Regex Fuzzing Capabilities}
\fuzzer{} can generate
and transform instances with regular expression constraints. For example, the
command \texttt{stringfuzzg regex} invokes the regex instance
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

\fuzzer{} can also transform problem instances.
This is done by manipulating parsed syntax trees.
By default most of the built-in transformers 
only guarantee well-formedness, however,
some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
lists the built-in transformers and notes these guarantees.

>>>>

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}
We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project
contains \linesInFuzzer{} lines of code, it takes an average of
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be
installed from source, or from the Python PIP package
repository.\footnote{The link to the source code will be added after double-blind review.}

@@

\subsubsection{Regex Generating Capabilities}
\fuzzer{} can generate
and transform instances with regular expression constraints. For example,
\texttt{stringfuzzg regex} invokes the regex
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

\subsubsection{Equisatisfiable String Transformations}
\fuzzer{} can also transform problem instances.
This is done by manipulating parsed syntax trees.
By default most of the built-in transformers
only guarantee well-formedness, however,
some can even guarantee equisatisfiability. Table~\ref{tbl:transformers}
lists the built-in transformers and notes these guarantees.
